Verification of Stencil Computations through Spatial Specifications

### 2016-07-06 paper.tex
conclusion needed...
added some words about introducing errors in the um stencil

% != stencil readOnce, (forward(depth=1, dim=3, irreflexive))*(backward(depth=1, dim=1))*(backward(depth=1, dim=2)) + (forward(depth=1, dim=3))*(backward(depth=1, dim=1))*(reflexive(dim=2)) + (forward(depth=1, dim=3))*(backward(depth=1, dim=1, irreflexive))*(backward(depth=1, dim=2, irreflexive)) + (forward(depth=1, dim=3))*(backward(depth=1, dim=2))*(reflexive(dim=1)) + (backward(depth=1, dim=1))*(backward(depth=1, dim=2, irreflexive))*(reflexive(dim=3)) + (backward(depth=1, dim=1, irreflexive))*(backward(depth=1, dim=2))*(reflexive(dim=3)) :: cx_rho_centre
% /um/trunk/src/atmosphere/diffusion_and_filtering/turb_smagorinsky.F90
% Tried introducing indexing errors replacing one of the indices of cx_rho_instance with -1,0,+1
% 42 cases were caught
% 6 cases were not caught

@@

>>>>

\subsubsection{Turbulence calculation}

The Unified Model contains an implementation of the Smagorinsky subgrid-scale model for calculating turbulence. The source file in question yields 38 stencils from 340 lines of code. We selected one as an example:

\begin{minted}[breakindent=8.1em]{fortran}
 != stencil readOnce, (forward(depth=1, dim=3, irreflexive))*(backward(depth=1, dim=1))*(backward(depth=1, dim=2)) + (forward(depth=1, dim=3))*(backward(depth=1, dim=1))*(reflexive(dim=2)) + (forward(depth=1, dim=3))*(backward(depth=1, dim=1, irreflexive))*(backward(depth=1, dim=2, irreflexive)) + (forward(depth=1, dim=3))*(backward(depth=1, dim=2))*(reflexive(dim=1)) + (backward(depth=1, dim=1))*(backward(depth=1, dim=2, irreflexive))*(reflexive(dim=3)) + (backward(depth=1, dim=1, irreflexive))*(backward(depth=1, dim=2))*(reflexive(dim=3)) :: x
\end{minted}

This stencil specifies the access pattern to a 3-dimensional array (which we have renamed to be called \texttt{x}). The array is accessed 8 times in the computation. We tried introducing indexing errors by changing the offset in one dimension of one of the references to \texttt{x}. For example changing \mintinline{fortran}{x(i+1,j,k)} to \mintinline{fortran}{x(i,j,k)} or \mintinline{fortran}{x(i-1,j,k)}. There are 48 possible errors of this type of which we found only 6 were not detected by the stencil check.
% /um/trunk/src/atmosphere/diffusion_and_filtering/turb_smagorinsky.F90
% Tried introducing indexing errors replacing one of the indices of cx_rho_instance with -1,0,+1
% 42 cases were caught
% 6 cases were not caught

@@

\section{Conclusion}

\anote{We need a conclusion!}
